---
title: "star layer for ggplot2"
author: |
  | Shuangbin Xu 
  | School of Basic Medical Sciences, Southern Medical University
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    toc: true
    theme: cayman
    highlight: vignette
  pdf_document:
    toc: true
vignette: >
  %\VignetteIndexEntry{ ggstar: basics using.}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
  %\VignetteEncoding{UTF-8}
---

```{r, echo=FALSE, results="asis", message=FALSE, KnitrSetUp}
knitr::opts_chunk$set(tidy=FALSE,warning=FALSE,message=FALSE)
Biocpkg <- function (pkg){
    sprintf("[%s](http://bioconductor.org/packages/%s)", pkg, pkg)
}

CRANpkg <- function(pkg){
    cran <- "https://CRAN.R-project.org/package" 
    fmt <- "[%s](%s=%s)"
    sprintf(fmt, pkg, cran, pkg) 
}
```

```{r, echo=FALSE, results="hide", message=FALSE, Loadpackages}
library(ggplot2)
library(ggstar)
```

# 1. Introduction

`ggstar` provides geoms for `r CRANpkg("ggplot2")` to create more easily discernible shapes:

`geom_star`

```{r, fig.width=5, fig.height=3, fig.align="center", starshapes}
p1 <- show_starshapes()
p1
```

And the default is: `c(1, 2, 9, 4, 3, 5, 6, 11, 12)[seq_len(n)]`. `n` is the number of shapes you want to use.

# 2. Install

`ggstar` hasn't been submitted on [CRAN](https://cran.r-project.org/), you can use the following to install it.

```r
# for devel
if(!requireNamespace("devtools", quietly=TRUE)){
    install.packages("remotes")
}
remotes::install_github("xiangpin/ggstar")
# for release
```

# 3. Usage

`geom_star` is similar to `geom_point` of `r CRANpkg("ggplot2")`. The difference point is `geom_star` use `starshape` to mapping the `starshapes`. The another is `geom_star` use `scale_starshape_manual` for manual scale. And the shapes will be not distorted on cartesian coordinates or polar coordinates.

## 3.1 Cartesian coordinates

```{r, fig.width=6, fig.height=5, fig.align="center", sizeshape}
library(ggplot2)
library(ggstar)
p2 <- ggplot(data=iris, aes(x=Sepal.Width,y=Sepal.Length)) + 
      geom_star(aes(starshape=Species, fill=Species), size=1.5) +
      scale_fill_manual(values=c("#E41A1C", "#377EB8", "#4DAF4A")) +
      theme(legend.spacing.y = unit(0.02, "cm"))
p2
```

## 3.2 Polar coordinates

```{r, fig.width=6, fig.height=5.2, fig.align="center", polarcoord}
p3 <- ggplot(data=mtcars, aes(x=wt, y=mpg)) +
      geom_star(aes(fill=cyl), size=1.5) +
      scale_fill_gradient(low="blue", high="red") +
      coord_polar() +
      theme(panel.border=element_blank(),
            legend.spacing.y = unit(0.02, "cm"))
p3
```

# 4. Need helps?

If you have questions/issues, please visit [github issue tracker](https://github.com/xiangpin/ggstar/issues).

# 5. Session information

Here is the output of sessionInfo() on the system on which this document was compiled:

```{r, echo=FALSE}
sessionInfo()
```
